Final Project

### 2020-11-27 chaloupka_sameshima_wallner_final_project.Rmd
add plots
ran new analysis of mean DT by seqpos2

>>>>

temp %>% 
  ggplot(aes(x = seq_pos2, y = dwell_time, color = fractal_type)) +
  geom_point(data = new_data_never, aes(y = mean_dwell_time)) +
  labs(y = "Dwell Time (s)", x = "Sequence Position", title = "Unfolding Dwell Times Over Sequential Fractal Iteration", subtitle = "by Fractal Type") +
  scale_y_continuous(limits = c(0, 1.4)) +
  geom_line(data = new_data_never, aes(y = mean_dwell_time)) +
  theme(legend.position = "none") +
  scale_color_viridis_d()

temp2 <- temp %>% 
  group_by(seq_pos2) %>% 
  summarise(mean_dt = mean(dwell_time)) %>% 
  mutate(mean_dt = mean_dt)

temp2 %>% 
  ggplot(aes(x = seq_pos2, y = mean_dt)) +
  geom_point(data = temp2, aes(y = mean_dt)) +
  labs(y = "Dwell Time (s)", x = "Sequence Position", title = "Unfolding Dwell Times Over Sequential Fractal Iteration", subtitle = "by Fractal Type") +
  scale_y_continuous(limits = c(0, 1.4)) +
  theme(legend.position = "none") +
  scale_color_viridis_d()
